Roster Review (Generic)

### 2019-05-15 rosterReview_generic.Rmd
Added position aggregation

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190429.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190429.csv", "pitcher")

@@

rosters_with_adj_projections <- rosters_with_projections %>% 
  filter(!type == 'NA') %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))
```

@@

```{r}
# TODO find way to wrap these three views into one
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Hebrew",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("deGrom|Rizzo",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters_with_adj_projections %>% 
  filter(!grepl("Free Agent",team),
         # grepl("SP|3B",display_position)
         ) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_boxplot() +
  # geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
rosters_with_adj_projections %>% 
  filter(!is.na(draft_pick)) %>%
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar_median))

>>>>

proj_batter <- add_z_scores_to_projections("data/depthChartProjections_ros_batters_20190513.csv","batter") 
proj_pitcher <- add_z_scores_to_projections("data/depthChartProjections_ros_pitchers_20190513.csv", "pitcher")

@@

rosters_with_adj_projections <- rosters_with_projections %>% 
  filter(!type == 'NA') %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))

position_columns <- rosters_with_adj_projections %>%
    select(starts_with("eligible_positions")) %>%
    colnames()

rosters_with_adj_projections %>%
  mutate(positions = paste(!!! syms(position_columns), sep = "," )) %>%
  mutate(positions = gsub('NA', '', positions)) %>%
  mutate(positions = gsub("^,*|(?<=,),|,*$", "", positions, perl=T)) %>%
  select(-(starts_with("eligible_positions"))) -> rosters_with_adj_projections
```

@@

```{r}
# TODO find way to wrap these three views into one
rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Utleys",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|Utleys",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters_with_adj_projections %>% 
  filter(grepl("Plouffe|theriverbrew",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("deGrom|Lucchesi",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

```{r}
rosters_with_adj_projections %>% 
  filter(!grepl("Free Agent",team),
  grepl("CF",positions)
       ) %>%
  ggplot(aes(x=team,y=zar,color=type)) +
  #geom_boxplot() +
  geom_jitter(aes(text=name_full), width = .2) +
  coord_flip() -> tb

@@

```{r}
#TODO measuring projected value of draft picks, move to separate research
rosters_with_adj_projections %>% 
  filter(!is.na(draft_pick)) %>%
  group_by(draft_round) %>% 
  summarize(zar_median = median(zar) %>% janitor::round_half_up(),
            zar_mean = mean(zar) %>% janitor::round_half_up()) %>%
  ggplot(aes(x=draft_round,y=zar_mean)) +
  geom_col() +
  geom_line(aes(y=zar_median)) -> draft_plot

ggplotly(draft_plot)
